---
title: Risk Model Validation and Refinement for Groin SSI after revascularization for PAD
author: Hana Shafique and Adam Johnson
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  word_document:
knit: (function(input, ...) {rmarkdown::render(input, output_file = paste0(tools::file_path_sans_ext(basename(input)), '-', Sys.Date(), '.docx'), output_dir = "reports")})
---

# Purpose Statement:

This project aims externally validate previously developed risk models for surgical site infection, following open lower extremity revascularization for peripheral artery disease through a groin incision.

# Data:

The national Vascular Quality Initiative suprainguinal and infrainguinal registries from 2011-2023 were queried for open lower extremity revascularizations that included a groin incision for femoral artery exposure with an indication of peripheral occlusive disease.

```{r packages, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(finalfit)
library(tidymodels)
library(probably)
library(pROC)
library(survival)
library(survminer)
library(predtools)
library(magrittr)
library(Hmisc)
library(labelled)
library(renv)
library(boot)
library(parallel)

#Create functions
source("code/functions.R")

#utils::sessionInfo()
```

```{r import and select relevant variables, echo=FALSE, warning=FALSE, message=FALSE}
#First we load data exported from "pad-grnssi-vqi-1select.rmd."  We keep this data outside this project as it is used by many different projects.
vqi_pad_grninf_clean <- readRDS("../../DataRepo/VQI/Analysis Data Files/vqi_pad.rds")

grninf_preop_v <- c("POSTOP_SSI","GRAFTINF","RTOR","RTORINF", "WCOMP", "POSTOP_LOS",
                    "PRIMPROCID","REGIONID","CENTERID","PHYSICIANID","PATIENTID",
                    "RUCA1","RUCA2","ADI_NATRANK_MEDIAN",
                    "SURGYEAR","SURGMONTH","SURGWEEKDAY","GENDER","RACE","HTCM","WTKG",
                    "PRIMARYINSURER","ETHNICITY","AGE", "TRANSFER",
                    "PRIOR_CVD","PREOP_SMOKING","HX_SMOKING_COUNSELING","QUIT_SMKG_DAYS",
                    "HTN","DIABETES","HBA1C",
                    "R_PRIOR_BYPASS","PRIOR_CEACAS","R_PRIOR_CEA","R_ANEURREP","PRIOR_ANEURREP",
                    "EXERCISE_PROGRAM","R_PTASTENT","R_PRIOR_MAJAMP",
                    "CAD","PRIOR_CABG","PRIOR_PCI","R_PRIOR_CABGPTCA","PRIOR_CHF","PREOP_DYSRHYTHMIA","COPD",
                    "DIALYSIS","CREATININE","STRESS",
                    "LIVINGSTATUS","PREOP_FUNCSTATUS","PREOP_AMBUL","ASACLASS","HEMO",
                    "PREOP_ASA","PREOP_P2Y","PREOP_STATIN","PREOP_BETABLOCKER","PREOP_ACE",
                    "PREOP_DUPLEX","PREOP_MRA","PREOP_CTA",
                    "POS_COVID_STAT","SIDE","C_PREOP_ANTICOAG",
                    "indication",
                    "R_INDICATIONR","R_INDICATIONL",
                    "INDICATION_OCCLUSIVE_R","INDICATION_OCCLUSIVE_L","INDICATION_ANEURYSM_R",
                    "INDICATION_ANEURYSM_L","ACUTE_ISCHEMIA_R","ACUTE_ISCHEMIA_L",
                    "TISSUE_LOSS_SEV_R","TISSUE_LOSS_SEV_L", "INFECTION_R","INFECTION_L",
                    "PINBYPASSR","PINBYPASSL","PINPTASTENTR","PINPTASTENTL",
                    "PLEGBYPASSR","PLEGBYPASSL", "PLEGPTASTENTR","PLEGPTASTENTL",
                    "R_PMAJAMPR","R_PMAJAMPL","R_PMINAMPR","R_PMINAMPL",
                    "AMPUTATION_HX_R","AMPUTATION_HX_L","PREOP_ABIR","PREOP_ABIL",
                    "PREOP_TOEPRESSURE_R","PREOP_NOTOE_R","PREOP_TOEPRESSURE_L","PREOP_NOTOE_L",
                    "PREOP_TCPO2_R","PREOP_NOTCPO2_R","PREOP_TCPO2_L","PREOP_NOTCPO2_L",
                    "R_PREOP_TBIR","ARTERIO","VMAP","R_PREOP_TBIL",
                    "GLASS_REGION_FEMOROPOPLITEAL","GLASS_REGION_INFRAPOPLITEAL",
                    "GLASS_REGION_INFRAMALEO_PEDAL","URGENCY",
                    "R_ANESTHESIA","ANESTHESIA_LOCAL","ANESTHESIA_CONSCIOUS_SEDATION",
                    "ANESTHESIA_REGIONAL","ANESTHESIA_GENERAL","SKINPREP","CHLOHEXIDINE_SHOWER",
                    "proc", "fem_exposure",
                    "GRAFTORIG","GRAFTRECIP","GRFTVTYPE","VEINSEG","PROSTHETIC",
                    "R_GRAFTVEINTYPE","R_VEINSEGS","R_PROSTHETIC",
                    "TOTALPROCTIME","GROIN_INCISION","CLOSURE",
                    "DRESSING_1","DRESSING_2","DRESSING_3","DRESSING_4",
                    "NEGATIVE_PRESSURE_DEVICE","R_VEIN_HARVEST_INCISION",
                    "R_VEIN_GRAFT_LOCATION","VEIN_HARVEST_INCISION","VEIN_GRAFT_LOCATION",
                    "R_VEINCUFF","SEQGRAFT","R_CCPVI","CC_IPS_PVI",
                    "R_CCENDAR","CC_IPS_ENDAR","CCBYPASS",
                    "SMOKING_CESS_RX_0","SMOKING_CESS_RX_1",
                    "SMOKING_CESS_RX_2","SMOKING_CESS_RX_3",
                    "R_ANTIBIOTICGEN", "R_ANTIBIOTICSTART","R_ANTIBIOTICEND",
                    "ABX","ABX_START","ABX_STOP",
                    "PREOP_NOABI_R","PREOP_NOABI_L",
                    "TASC_GRADE_AORTO_ILIAC_R","TASC_GRADE_AORTO_ILIAC_L",
                    "TASC_GRADE_FEM_POPLITEAL_R","TASC_GRADE_FEM_POPLITEAL_L",
                    "TASC_GRADE_INFRAPOPLITEAL_R","TASC_GRADE_INFRAPOPLITEAL_L",
                    "INCISION_SIDE","GROIN_INCISION_R","GROIN_INCISION_L",
                    "CLOSURE_R","CLOSURE_L",
                    "DRESSING_R_1","DRESSING_R_2","DRESSING_R_3","DRESSING_R_4",
                    "DRESSING_L_1","DRESSING_L_2","DRESSING_L_3","DRESSING_L_4",
                    "NEGATIVE_PRESSURE_DEVICE_R","NEGATIVE_PRESSURE_DEVICE_L",
                    "GRFT_ORIGIN_ARTERY","SURGERYSIDE","GRFT_ORIGIN_DIA",
                    "GRFT_RECP1_ARTERY","GRFT_RECP1_SIDE","GRFT_RECP1_GRFT_DIA",
                    "GRFT_RECP1_GRFT_TYPE","GRFT_RECP1_ENDART",
                    "GRFT_RECP2_ARTERY","GRFT_RECP2_SIDE","GRFT_RECP2_GRFT_DIA",
                    "GRFT_RECP2_GRFT_TYPE","GRFT_RECP2_ENDART",
                    "CCBYPASS_R","CCBYPASS_L","CCPVI_R","CCPVI_L","proc_ler","proc_ai")

vqi_pad_grninf_preop_proc <- vqi_pad_grninf_clean[, grninf_preop_v, drop = FALSE]

rm(list = c("vqi_pad_grninf_clean", "grninf_preop_v"))

```

# Variable Definitions

We define our outcome as a binary variable inclusive of superficial, deep and organ space surgical site infection, necrosis, dehiscence, or lymph leak that required treatment with antibiotics, reoperation or readmission during the index admission or at any point during follow up.

```{r outcome, echo=FALSE, warning=FALSE, message=FALSE}

# We will define SSI as reported anytime during following.  Some LTF dates are >1 year and report an SSI, however unclear the timing of the actual SSI.

# Import and clean data from LTF data sets
source("code/vasc_fem_inf_vqi_clean_infra_ltf.R")
infra_ltf_grninf <- infra_ltf %>% select(allVars_infra_ltf)

source("code/vasc_fem_inf_vqi_clean_supra_ltf.R")
supra_ltf_grninf <- supra_ltf %>% select(allVars_supra_ltf)

pad_ltf_grninf <- bind_rows(infra_ltf_grninf,supra_ltf_grninf)

rm(list = c("infra_ltf", "supra_ltf", "infra_ltf_grninf", "supra_ltf_grninf"))

# Create Groin SSI variable

pad_ltf_grninf$grninf_ltf <- ifelse(pad_ltf_grninf$D30_SSI == "Superficial" |
                                        pad_ltf_grninf$D30_SSI == "Deep" |
                                        pad_ltf_grninf$D30_SSI == "Organ Space" |
                                        pad_ltf_grninf$R_D30_SSI == "Superficial" |
                                        pad_ltf_grninf$R_D30_SSI == "Deep" |
                                        pad_ltf_grninf$R_D30_SSI == "Organ Space" |
                                        pad_ltf_grninf$LTF_SSI == "Superficial" |
                                        pad_ltf_grninf$LTF_SSI == "Deep" |
                                        pad_ltf_grninf$LTF_SSI == "Organ Space" |
                                        pad_ltf_grninf$R_D30_GRAFT == TRUE |
                                        pad_ltf_grninf$LTF_SSIGRAFT == TRUE |
                                        pad_ltf_grninf$D30_ADMISSION_REASON == "Surgical Site Infection" |
                                        pad_ltf_grninf$D30_ADMISSION_REASON == "Wound Complication" |
                                        pad_ltf_grninf$D30_WOUNDCOMP_NECROSIS == TRUE |
                                        pad_ltf_grninf$D30_WOUNDCOMP_DEHISCENCE == TRUE |
                                        pad_ltf_grninf$D30_WOUNDCOMP_LYMPH_LEAK == TRUE,
                                        TRUE, FALSE)
pad_ltf_grninf$grninf_ltf <- replace(pad_ltf_grninf$grninf_ltf, is.na(pad_ltf_grninf$grninf_ltf), FALSE)
pad_ltf_grninf$grninf_ltf <- as.logical(pad_ltf_grninf$grninf_ltf)

pad_ltf_grninf$s_grninf_ltf <- ifelse(pad_ltf_grninf$D30_SSI == "Deep" |
                                        pad_ltf_grninf$D30_SSI == "Organ Space" |
                                        pad_ltf_grninf$R_D30_SSI == "Deep" |
                                        pad_ltf_grninf$R_D30_SSI == "Organ Space" |
                                        pad_ltf_grninf$LTF_SSI == "Deep" |
                                        pad_ltf_grninf$LTF_SSI == "Organ Space" |
                                        pad_ltf_grninf$R_D30_GRAFT == TRUE |
                                        pad_ltf_grninf$LTF_SSIGRAFT == TRUE |
                                        pad_ltf_grninf$D30_ADMISSION_REASON == "Surgical Site Infection" |
                                        pad_ltf_grninf$D30_ADMISSION_REASON == "Wound Complication" |
                                        pad_ltf_grninf$D30_WOUNDCOMP_NECROSIS == TRUE |
                                        pad_ltf_grninf$D30_WOUNDCOMP_DEHISCENCE == TRUE |
                                        pad_ltf_grninf$D30_WOUNDCOMP_LYMPH_LEAK == TRUE,
                                        TRUE, FALSE)
pad_ltf_grninf$s_grninf_ltf <- replace(pad_ltf_grninf$s_grninf_ltf, is.na(pad_ltf_grninf$s_grninf_ltf), FALSE)
pad_ltf_grninf$s_grninf_ltf <- as.logical(pad_ltf_grninf$s_grninf_ltf)

# Survival analysis for Groin SSI

## Identifying date where SSI was first reported.
pad_ltf_grninf_surv = pad_ltf_grninf %>%
  select(c(PRIMPROCID, LTF_DAYS, grninf_ltf))

pad_ltf_grninf_surv$grninf_surv[pad_ltf_grninf_surv$grninf_ltf == TRUE] <- 1
pad_ltf_grninf_surv$grninf_surv[pad_ltf_grninf_surv$grninf_ltf == FALSE] <- 0

pad_ltf_grninf_surv_trim = pad_ltf_grninf_surv %>% 
  arrange(PRIMPROCID, LTF_DAYS) %>% 
  group_by(PRIMPROCID) %>% 
  mutate(
    first_event = cumsum(grninf_surv) == 1,      # Mark TRUE if goes from 0 to 1
    status_nochange = sum(grninf_surv) == 0,                       # Mark if no change from 0
    status_nochange_keep = !duplicated(status_nochange, fromLast= TRUE) # Mark most recent "no change" episode
  ) %>% 
  filter(first_event | (status_nochange & status_nochange_keep)) %>%  # Filter out other episodes
  select(-c(first_event, status_nochange, status_nochange_keep))      # Remove columns not needed

## Identifying date where severe SSI was first reported.
pad_ltf_s_grninf_surv = pad_ltf_grninf %>%
  select(c(PRIMPROCID, LTF_DAYS, s_grninf_ltf))

pad_ltf_s_grninf_surv$s_grninf_surv[pad_ltf_s_grninf_surv$s_grninf_ltf == TRUE] <- 1
pad_ltf_s_grninf_surv$s_grninf_surv[pad_ltf_s_grninf_surv$s_grninf_ltf == FALSE] <- 0

pad_ltf_s_grninf_surv_trim = pad_ltf_s_grninf_surv %>% 
  arrange(PRIMPROCID, LTF_DAYS) %>% 
  group_by(PRIMPROCID) %>% 
  mutate(
    first_event = cumsum(s_grninf_surv) == 1,      # Mark TRUE if goes from 0 to 1
    status_nochange = sum(s_grninf_surv) == 0,                       # Mark if no change from 0
    status_nochange_keep = !duplicated(status_nochange, fromLast= TRUE) # Mark most recent "no change" episode
  ) %>% 
  filter(first_event | (status_nochange & status_nochange_keep)) %>%  # Filter out other episodes
  select(-c(first_event, status_nochange, status_nochange_keep))      # Remove columns not needed

#Merge the LTF and PROC datasets

vqi_pad_grninf_preop_grninf <- merge(vqi_pad_grninf_preop_proc, pad_ltf_grninf_surv_trim, by='PRIMPROCID')
vqi_pad_grninf_preop <- merge(vqi_pad_grninf_preop_grninf, pad_ltf_s_grninf_surv_trim, by='PRIMPROCID')

#Define the PROC SSI

vqi_pad_grninf_preop$grninf_proc <- ifelse(vqi_pad_grninf_preop$POSTOP_SSI == "TRUE" |
                                        vqi_pad_grninf_preop$GRAFTINF == "TRUE" |
                                        vqi_pad_grninf_preop$RTORINF == "TRUE" |
                                        vqi_pad_grninf_preop$WCOMP == "Superficial Separation / Infection" |
                                        vqi_pad_grninf_preop$WCOMP == "Return to OR",
                                        TRUE, FALSE)
vqi_pad_grninf_preop$grninf_proc <- replace(vqi_pad_grninf_preop$grninf_proc, is.na(vqi_pad_grninf_preop$grninf_proc), FALSE)
vqi_pad_grninf_preop$grninf_proc <- as.logical(vqi_pad_grninf_preop$grninf_proc)

vqi_pad_grninf_preop$s_grninf_proc <- ifelse(vqi_pad_grninf_preop$GRAFTINF == "TRUE" |
                                        vqi_pad_grninf_preop$RTORINF == "TRUE" |
                                        vqi_pad_grninf_preop$WCOMP == "Return to OR",
                                        TRUE, FALSE)
vqi_pad_grninf_preop$s_grninf_proc <- replace(vqi_pad_grninf_preop$s_grninf_proc, is.na(vqi_pad_grninf_preop$s_grninf_proc), FALSE)
vqi_pad_grninf_preop$s_grninf_proc <- as.logical(vqi_pad_grninf_preop$s_grninf_proc)


# Create grninf variable that includes both inpatient and outpatient grn infections.
vqi_pad_grninf_preop$grninf <- ifelse(vqi_pad_grninf_preop$grninf_proc == TRUE, TRUE, vqi_pad_grninf_preop$grninf_ltf)

vqi_pad_grninf_preop$s_grninf <- ifelse(vqi_pad_grninf_preop$s_grninf_proc == TRUE, TRUE, vqi_pad_grninf_preop$s_grninf_ltf)

# Assign the time variable to LOS if SSI occurs inpatient and set to LTF days if occurs as an outpatient.
#vqi_pad_grninf_preop$time <- ifelse(vqi_pad_grninf_preop$grninf_proc == TRUE, vqi_pad_grninf_preop$POSTOP_LOS, vqi_pad_grninf_preop$LTF_DAYS)

# Create Kaplan Meier Curve

#fit <- survfit(Surv(time = vqi_pad_grninf_preop$time, event = vqi_pad_grninf_preop$grninf) ~ 1, data = vqi_pad_grninf_preop)

#ggsurvplot(fit, data = vqi_pad_grninf_preop,
#           title = "Groin SSI after Open LER",
#           xlab = "Time",
#           ylab = "Survival Probability")
#summary(fit, times = c(0, 30, 90, 365, 730))

rm(list = c("infra_ltf_grninf", "pad_ltf_grninf", "supra_ltf", "supra_ltf_grninf", "vqi_ltf_grninf",
            "vqi_pad_grninf_preop_proc", "allVars_infra_ltf", "allVars_supra_ltf", "pad_ltf_grninf_surv",
            "pad_ltf_grninf_surv_trim"))

vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("grninf_ltf", "s_grninf_ltf", "grninf_proc", "s_grninf_proc"))]

#vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("POSTOP_SSI", "GRAFTINF", "RTOR", "RTORINF", "WCOMP", #'POSTOP_LOS', 'LTF_DAYS', 'LTF_SSIGRAFT', 'D30_WOUNDCOMP_NECROSIS', 'D30_WOUNDCOMP_HEMATOMA', 'D30_WOUNDCOMP_SEROMA', 'D30_WOUNDCOMP_LYMPH_LEAK', #'D30_WOUNDCOMP_DEHISCENCE', 'D30_WOUNDCOMP_OTHER',            'D30_VASCCOMP_BLEEDING', 'R_D30_GRAFT', 'LTF_SSI','FWP_TIMEPOINT', #'D30_ADMISSION_REASON', 'D30_SSI', 'R_D30_SSI', 'grninf_ltf', 'grninf_surv','grninf_proc'))]

#Select for centers who report more than 10 events

#center_events <- table(vqi_pad_grninf_preop$CENTERID, vqi_pad_grninf_preop$grninf)
#center_events <- as.data.frame(center_events)

#center_grninf <- center_events %>%
#  filter(Var2 == TRUE & Freq >= 10)

#centers_grt10 <- center_grninf$Var1

#vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
#  filter(CENTERID %in% centers_grt10)

```

Table 1: VQI cohort patient demographics.

```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}

vqi_pad_grninf_preop <- droplevels(vqi_pad_grninf_preop)

#Label the variables for the table - need to use "ff_label" no the labelled package.
vqi_pad_grninf_preop$AGE %>%
  ff_label("Age in Years") %>%
  str()
vqi_pad_grninf_preop$GENDER %>%
  ff_label("Sex") %>%
  str()
vqi_pad_grninf_preop$RACE %>%
  ff_label("Race") %>%
  str()
vqi_pad_grninf_preop$SURGYEAR %>%
  ff_label("Operative Year") %>%
  str()
vqi_pad_grninf_preop$indication %>%
  ff_label("Indication") %>%
  str()
vqi_pad_grninf_preop$proc %>%
  ff_label("Procedure") %>%
  str()

t1_exp <- c("AGE", "GENDER", "RACE", "indication", "proc")
dep_1 <- "grninf"
dep_2 <- "s_grninf"
vqi_pad_grninf_preop %>%
  summary_factorlist(dep_1, t1_exp,
                     add_col_totals = TRUE,
                     include_col_totals_percent = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N=",
                     total_col = TRUE) -> t1_1

t1_1 <- t1_1 %>%
  select(1, 2, 4, 5) %>%
  rename("Any Groin SSI" = "TRUE")

vqi_pad_grninf_preop %>%
  summary_factorlist(dep_2, t1_exp,
                     add_col_totals = TRUE,
                     include_col_totals_percent = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N=",
                     total_col = TRUE) -> t1_2

t1_2 <- t1_2 %>%
  select(4) %>%
  rename("Severe Groin SSI" = "TRUE")

t1 <- t1_1 %>%
  bind_cols(t1_2) %>%
  select(1, 2, 3, 5, 4)

knitr::kable(t1, align = c("l", "l", "r", "r", "r"))
```

# Variable Mapping

We included studies identified through two previously published systematic reviews (Gwilym et al and Kirkham et al). We mapped each feature to the variables collected in the VQI registry. We attempted direct mapping when the variable definitions aligned sufficiently. In the case that no direct mapping was possible, we attempted to create a proxy feature that aligned with the conceptual definition of the variable included in the study. When no variable was available that aligned with the published feature we excluded this variable from the model, imputing for the reference.

## Demographics

```{r Demographics, echo=FALSE, warning=FALSE, message=FALSE}

#Create an object for current column names
column_names_no_demo <- colnames(vqi_pad_grninf_preop)

# Age, dichotomized in different models - Wiseman, Kalish, Xu

  vqi_pad_grninf_preop$age1845 <- ifelse(vqi_pad_grninf_preop$AGE > "18" & vqi_pad_grninf_preop$AGE < "45", TRUE, FALSE)
  vqi_pad_grninf_preop$age1845 <- ifelse(is.na(vqi_pad_grninf_preop$age1845), 
                                       FALSE, vqi_pad_grninf_preop$age1845)
  label(vqi_pad_grninf_preop$age1845) <- "Age 18-45"

  vqi_pad_grninf_preop$age4565 <- ifelse(vqi_pad_grninf_preop$AGE > "45" & vqi_pad_grninf_preop$AGE < "65", TRUE, FALSE)
  vqi_pad_grninf_preop$age4565 <- ifelse(is.na(vqi_pad_grninf_preop$age4565), 
                                       FALSE, vqi_pad_grninf_preop$age4565)
  label(vqi_pad_grninf_preop$age4565) <- "Age 45-65"

  ##Create variable for age greater than 65. - Wiseman
  vqi_pad_grninf_preop$age65 <- ifelse(vqi_pad_grninf_preop$AGE > "65", TRUE, FALSE)
  label(vqi_pad_grninf_preop$age65) <- "Age >65"

  ## Xu dichotomizes age at 73
  vqi_pad_grninf_preop$age73 <- ifelse(vqi_pad_grninf_preop$AGE >= "73", TRUE, FALSE)
  label(vqi_pad_grninf_preop$age73) <- "Age >=73"


# Sex, female - Xu, Bennett, Wiseman, Gwilym - Deep

  vqi_pad_grninf_preop$female <- ifelse(vqi_pad_grninf_preop$GENDER == "Female", TRUE, FALSE)
  label(vqi_pad_grninf_preop$female) <- "Female Sex"
  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("GENDER"))]


# Race Ethnicity - Wiseman, Xu

  ## Xu utilizes non-hispanic white as a variable
  vqi_pad_grninf_preop$whtrace <- ifelse(vqi_pad_grninf_preop$RACE == "White" &
                                         vqi_pad_grninf_preop$ETHNICITY == FALSE, TRUE, FALSE)
  vqi_pad_grninf_preop$whtrace <- ifelse(is.na(vqi_pad_grninf_preop$whtrace), 
                                        FALSE, vqi_pad_grninf_preop$whtrace)
  label(vqi_pad_grninf_preop$whtrace) <- "Non-hispanic White"

  ##Create Black and Other race variable from on race variable in NSQIP. - Wiseman
  vqi_pad_grninf_preop$blkrace <- ifelse(vqi_pad_grninf_preop$RACE == "Black or African American", TRUE, FALSE)
  label(vqi_pad_grninf_preop$blkrace) <- "Black or African American"

  ##Other Race - Wiseman
  vqi_pad_grninf_preop$othrace <- ifelse(vqi_pad_grninf_preop$RACE == "American Indian or Alaskan Native" |
                                         vqi_pad_grninf_preop$RACE == "Asian" |
                                         vqi_pad_grninf_preop$RACE == "Native Hawaiian or other Pacific Islander" |
                                         vqi_pad_grninf_preop$RACE == "More than 1 race" |
                                         vqi_pad_grninf_preop$RACE == "Unknown / Other", TRUE, FALSE)
  label(vqi_pad_grninf_preop$othrace) <- "Other Race"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("RACE"))]

# BMI/Obesity - Xu, Sorour, Bennett, Kalish, Wiseman

  vqi_pad_grninf_preop$BMI <- vqi_pad_grninf_preop$WTKG/((vqi_pad_grninf_preop$HTCM/100)^2)
  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("WTKG", "HTCM"))]

  ## Bennett ans Wiseman Defines as overweight (25-30) or obese (>30), Sorour and Fischer uses BMI >30
  vqi_pad_grninf_preop$underweight <- ifelse(vqi_pad_grninf_preop$BMI < "18.5", TRUE, FALSE)
  vqi_pad_grninf_preop$underweight <- ifelse(is.na(vqi_pad_grninf_preop$underweight), 
                                           FALSE, vqi_pad_grninf_preop$underweight)
  label(vqi_pad_grninf_preop$underweight) <- "Underweight (BMI <18)"

  vqi_pad_grninf_preop$overweight <- ifelse(vqi_pad_grninf_preop$BMI > "25" & vqi_pad_grninf_preop$BMI < "30", TRUE, FALSE)
  vqi_pad_grninf_preop$overweight <- ifelse(is.na(vqi_pad_grninf_preop$overweight), 
                                          FALSE, vqi_pad_grninf_preop$overweight)
  label(vqi_pad_grninf_preop$overweight) <- "Overweight (BMI 25-30)"

  vqi_pad_grninf_preop$obese <- ifelse(vqi_pad_grninf_preop$BMI > "30", TRUE, FALSE)
  vqi_pad_grninf_preop$obese <- ifelse(is.na(vqi_pad_grninf_preop$obese), 
                                     FALSE, vqi_pad_grninf_preop$obese)
  label(vqi_pad_grninf_preop$obese) <- "Obese (BMI >30)"

  ##Create variable for BMI > 35 - Xu 
  vqi_pad_grninf_preop$BMI35 <- ifelse(vqi_pad_grninf_preop$BMI > "35", TRUE, FALSE)
  vqi_pad_grninf_preop$BMI35 <- ifelse(is.na(vqi_pad_grninf_preop$BMI35), 
                                     FALSE, vqi_pad_grninf_preop$BMI35)
  label(vqi_pad_grninf_preop$BMI35) <- "BMI > 35"
  
  ##Create variable for BMI > 40 - Aziz
  vqi_pad_grninf_preop$BMI40 <- ifelse(vqi_pad_grninf_preop$BMI > "40", TRUE, FALSE)
  vqi_pad_grninf_preop$BMI40 <- ifelse(is.na(vqi_pad_grninf_preop$BMI40), 
                                     FALSE, vqi_pad_grninf_preop$BMI40)
  label(vqi_pad_grninf_preop$BMI40) <- "BMI > 40"

# Smoking Status - Fischer, Bennett, Xu, Fischer

  vqi_pad_grninf_preop$smoke <- ifelse(vqi_pad_grninf_preop$PREOP_SMOKING == "Current", TRUE, FALSE)
  label(vqi_pad_grninf_preop$smoke) <- "Current Smoker"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("SMOKING"))]

# Functional Status - Xu, Wiseman, Eslami (mFI component)

  ## Totally dependent functional status (fnstatus2).Based on the variables PREOP_FUNCSTATUS and PREOP_AMBUL.  Ambulation 
  ## funcational status variable was added very recently and ambulation status will be used to infer funcitonal status. - Wiseman
  vqi_pad_grninf_preop$fnst_par <- ifelse(vqi_pad_grninf_preop$PREOP_FUNCSTATUS == "Assisted care" |
                                          vqi_pad_grninf_preop$PREOP_AMBUL == "Ambulates w/ assistance or prosthesis" |
                                          vqi_pad_grninf_preop$PREOP_AMBUL == "Ambulates w/ prosthesis" |
                                          vqi_pad_grninf_preop$PREOP_AMBUL == "Ambulates w/ assistance", TRUE, FALSE)
  vqi_pad_grninf_preop$fnst_par <- ifelse(is.na(vqi_pad_grninf_preop$fnst_par), 
                                        FALSE, vqi_pad_grninf_preop$fnst_par)
  label(vqi_pad_grninf_preop$fnst_par) <- "Partially Dependent Functional Status"

  vqi_pad_grninf_preop$fnst_dep <- ifelse(vqi_pad_grninf_preop$PREOP_FUNCSTATUS == "Bed bound" |
                                          vqi_pad_grninf_preop$PREOP_AMBUL == "Bedridden" |
                                          vqi_pad_grninf_preop$PREOP_AMBUL == "Wheelchair", TRUE, FALSE)
  vqi_pad_grninf_preop$fnst_dep <- ifelse(is.na(vqi_pad_grninf_preop$fnst_dep), 
                                        FALSE, vqi_pad_grninf_preop$fnst_dep)
  label(vqi_pad_grninf_preop$fnst_dep) <- "Fully Dependent Functional Status"

  ##We develop fnst_any from the variables developed for the Wiseman Model for the mFI in Eslami model

  vqi_pad_grninf_preop$fnst_any <- ifelse(vqi_pad_grninf_preop$fnst_dep == TRUE|
                                          vqi_pad_grninf_preop$fnst_par == TRUE, TRUE, FALSE)
  vqi_pad_grninf_preop$fnst_any <- ifelse(is.na(vqi_pad_grninf_preop$fnst_any), 
                                        FALSE, vqi_pad_grninf_preop$fnst_any)
  label(vqi_pad_grninf_preop$fnst_any) <- "Patrially or Full Dependent Functional Status"
  
  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("PREOP_FUNCSTATUS", "PREOP_AMBUL"))]

# Create an object for all new column names created in this code chunk
  
column_names_w_demo <- colnames(vqi_pad_grninf_preop)
demo_names <- setdiff(column_names_w_demo, column_names_no_demo)
  
#Create a table with frequencies for the demographic features

table_2outcome(vqi_pad_grninf_preop, demo_names, "grninf", "s_grninf")

```

## Comorbidities

```{r Comorbidity variables, echo=FALSE, warning=FALSE, message=FALSE}

col_no_comorbid <- colnames(vqi_pad_grninf_preop)

# Diabetes Mellitus - Xu, Sorour, Kalish, Wiseman, Gwilym - Deep, Eslami (mFI component)

  ## Model includes a variable for any diabetes - Gwylim - Deep, Eslami (mFI Component), Xu
  vqi_pad_grninf_preop$dm_any <- ifelse(vqi_pad_grninf_preop$DIABETES == "Insulin" |
                                        vqi_pad_grninf_preop$DIABETES == "Non-insulin meds" |
                                        vqi_pad_grninf_preop$DIABETES == "Diet",
                                      TRUE, FALSE)
  vqi_pad_grninf_preop$dm_any <- ifelse(is.na(vqi_pad_grninf_preop$dm_any), 
                                      FALSE, vqi_pad_grninf_preop$dm_any)
  label(vqi_pad_grninf_preop$dm_any) <- "Diabetese Mellitus"

  ## Create insulin dependent diabetes variable
  ## The false value represent the patients with diabetes who are not insulin dependent. - Wiseman,           Sorour
  vqi_pad_grninf_preop$dm_ins <- ifelse(vqi_pad_grninf_preop$DIABETES == "Insulin", TRUE, FALSE)
  vqi_pad_grninf_preop$dm_ins <- ifelse(is.na(vqi_pad_grninf_preop$dm_ins), 
                                      FALSE, vqi_pad_grninf_preop$dm_ins)
  label(vqi_pad_grninf_preop$dm_ins) <- "Diabetes Mellitus (Insulin Dependent)"

  vqi_pad_grninf_preop$dm_nonins <- ifelse(vqi_pad_grninf_preop$DIABETES == "Non-insulin meds" |
                                           vqi_pad_grninf_preop$DIABETES == "Diet", TRUE, FALSE)
  vqi_pad_grninf_preop$dm_nonins <- ifelse(is.na(vqi_pad_grninf_preop$dm_nonins), 
                                         FALSE, vqi_pad_grninf_preop$dm_nonins)
  label(vqi_pad_grninf_preop$dm_nonins) <- "Diabetes Mellitus (Non-Insulin Dependent)"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("DIABETES"))]

# COPD - Leekha, Sorour, Xu, Wiseman, Eslami (mFI component), Aziz

  ## Utilize hxCOPD variable for COPD. No need to create a new variable
  vqi_pad_grninf_preop$hxcopd <- ifelse(vqi_pad_grninf_preop$COPD == "Not treated" |
                                        vqi_pad_grninf_preop$COPD == "On meds" |
                                        vqi_pad_grninf_preop$COPD == "On home oxygen", TRUE, FALSE)
  label(vqi_pad_grninf_preop$hxcopd) <- "History of COPD"

  vqi_pad_grninf_preop$hxcopd_tx <- ifelse(vqi_pad_grninf_preop$COPD == "On meds" |
                                           vqi_pad_grninf_preop$COPD == "On home oxygen", TRUE, FALSE)
  label(vqi_pad_grninf_preop$hxcopd_tx) <- "History of COPD on treatment"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("COPD"))]

# Coronary Artery Disease/Cardiac History - Leekha, Wiseman, Eslami (included in mFI), Xu

  ## Create variable ischemic heart disease using multiple variables related to ischemic heart
  ## disease.  CAD, PRIOR_CABG, PRIOR_PCI are all related to ischemic heart disease.  We will not
  ## include HTN, PRIOR_CHF, and PREOP_DYSRHYTHMIA because these are heart diseases not necessarily
  ## related to underlying ischemic disease.

  vqi_pad_grninf_preop$CAD <- fct_explicit_na(vqi_pad_grninf_preop$CAD, na_level = "None")
  vqi_pad_grninf_preop$PRIOR_CABG <- fct_explicit_na(vqi_pad_grninf_preop$PRIOR_CABG, na_level = "None")
  vqi_pad_grninf_preop$PRIOR_PCI <- fct_explicit_na(vqi_pad_grninf_preop$PRIOR_PCI, na_level = "None")

  vqi_pad_grninf_preop$heart_dz <- ifelse(vqi_pad_grninf_preop$CAD == "Hx MI but no sx" | 
                                          vqi_pad_grninf_preop$CAD == "Stable angina" |
                                          vqi_pad_grninf_preop$CAD == "Unstable angina or MI < 6 mos (retired                                                                        since 09/12/2012)" |
                                          vqi_pad_grninf_preop$CAD == "MI < 6 mos" |
                                          vqi_pad_grninf_preop$CAD == "Unstable angina" |
                                          vqi_pad_grninf_preop$CAD == "CAD, asymptomatic" |
                                          vqi_pad_grninf_preop$PRIOR_CABG == "<5yr ago" |
                                          vqi_pad_grninf_preop$PRIOR_CABG == ">= 5yrs ago" |
                                          vqi_pad_grninf_preop$PRIOR_PCI == "<5yr ago" |
                                          vqi_pad_grninf_preop$PRIOR_PCI == ">= 5yrs ago" |
                                          vqi_pad_grninf_preop$R_PRIOR_CABGPTCA == "<5yr ago" |
                                          vqi_pad_grninf_preop$R_PRIOR_CABGPTCA == ">= 5yrs ago", TRUE, FALSE)
  vqi_pad_grninf_preop$heart_dz <- 
    replace(vqi_pad_grninf_preop$heart_dz, is.na(vqi_pad_grninf_preop$heart_dz), FALSE)
  label(vqi_pad_grninf_preop$heart_dz) <- "Ischemic Heart Disease"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) 
                                                    %in% c("CAD", "PRIOR_CABG","PRIOR_PCI",
                                                           "R_PRIOR_CABGPTCA"))]

  ## Xu includes a variable for the absence of CAD
  vqi_pad_grninf_preop$no_heart_dz <- ifelse(vqi_pad_grninf_preop$heart_dz == FALSE, TRUE, FALSE)


  ## Hypertension - Wiseman, Eslami (mFI Component)
  vqi_pad_grninf_preop$hypermed <- ifelse(vqi_pad_grninf_preop$HTN == "Yes (>=140/90 or history - retired since
                                                                      11/15/2016)" |
                                          vqi_pad_grninf_preop$HTN == "Yes, controlled [added on 04/13/2020]" |
                                          vqi_pad_grninf_preop$HTN == "Yes, uncontrolled [added on
                                                                        04/13/2020]", TRUE, FALSE)
  label(vqi_pad_grninf_preop$hypermed) <- "Hypertension"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("HTN"))]


  ## Congestive Heart Failure - Eslami (mFI component)
  vqi_pad_grninf_preop$CHF <- ifelse(vqi_pad_grninf_preop$PRIOR_CHF == "Asymptomatic, hx only" |
                                     vqi_pad_grninf_preop$PRIOR_CHF == "Mild" |
                                     vqi_pad_grninf_preop$PRIOR_CHF == "Moderate" |
                                     vqi_pad_grninf_preop$PRIOR_CHF == "Severe", TRUE, FALSE)
  label(vqi_pad_grninf_preop$CHF) <- "History of CHF"


# Cerebrovascular disease - Eslami, Wiseman

  ##Create variable for neurological disease, include history of stroke or TIA.  We will also include whether    they    have had a previous intervention for cerebrovascular disease.

  vqi_pad_grninf_preop$neuro <- ifelse(vqi_pad_grninf_preop$PRIOR_CVD == "Hx stroke, asymptomatic" |
                                       vqi_pad_grninf_preop$PRIOR_CVD == "Hx stroke, minor deficit" |
                                       vqi_pad_grninf_preop$PRIOR_CVD == "Hx stroke, major deficit" |
                                       vqi_pad_grninf_preop$PRIOR_CEACAS == "Yes" |
                                       vqi_pad_grninf_preop$PRIOR_CEACAS == "CEA" |
                                       vqi_pad_grninf_preop$PRIOR_CEACAS == "CAS" |
                                       vqi_pad_grninf_preop$PRIOR_CEACAS == "Both" |
                                       vqi_pad_grninf_preop$R_PRIOR_CEA == "TRUE", TRUE, FALSE)
  vqi_pad_grninf_preop$neuro <- replace(vqi_pad_grninf_preop$neuro, is.na(vqi_pad_grninf_preop$neuro), FALSE)
  label(vqi_pad_grninf_preop$neuro) <- "History of Cerebrovascular Disease"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("PRIOR_CVD",
                                                                                       "PRIOR_CEACAS",
                                                                                       "R_PRIOR_CEA"))]

# ESRD or CKD - Bennett, Eslami

  ## Bennett et al defines as a diagnosis of End Stage Renal Disease.  We will use DIALYSIS variable.  We will lump
  ## transplants in with dialysis patients.  Only small number with functioning transplant so not reasonable to 
  ## treat as their own group
  vqi_pad_grninf_preop$esrd <- ifelse(vqi_pad_grninf_preop$DIALYSIS == "On dialysis" |
                                      vqi_pad_grninf_preop$DIALYSIS == "Functioning transplant", TRUE, FALSE)
  label(vqi_pad_grninf_preop$esrd) <- "ESRD (On dialysis or functioning transplant)"

  ## We will create binary variables for different values of Cr 1.5-2 and >2 - Eslami
  vqi_pad_grninf_preop$cr_152 <- 
    ifelse(vqi_pad_grninf_preop$CREATININE > 1.5 & vqi_pad_grninf_preop$CREATININE < 2, TRUE, FALSE)
  label(vqi_pad_grninf_preop$cr_152) <- "Creatinine 1.5-2.0 mg/dL"
  vqi_pad_grninf_preop$cr_gr2 <- ifelse(vqi_pad_grninf_preop$CREATININE >= 2, TRUE, FALSE)
  label(vqi_pad_grninf_preop$cr_gr2) <- "Creatinine >2.0 mg/dL"

# Malnutrition - Bennett

  ## Bennett et al defines malnutrition according to ICD-9 codes: 262, 263, 263.1, 263.9
  ## Create a variable for malnutrition based what components are available from PONS (Wischmeyer et al 2018), the       components of which are:
  ## BMI < 18.5; Weightloss >10% in last 6mo; Reduced oral intake by 50% in past week; Preop serum albumin <3.0 g/dL
  ## VQI only includes BMI, so we will use that alone for malnutrtion.

  vqi_pad_grninf_preop$malnut <- ifelse(vqi_pad_grninf_preop$BMI < "18.5", TRUE, FALSE)
  label(vqi_pad_grninf_preop$malnut) <- "Malnutrition"

# Immunosuppresion - Sorour - not available in the VQI data set

# Frailty Index - Create 5 variable modified frailty index - Eslami
  vqi_pad_grninf_preop$mFI = (vqi_pad_grninf_preop$fnst_any + vqi_pad_grninf_preop$dm_any + 
                                vqi_pad_grninf_preop$hxcopd + vqi_pad_grninf_preop$CHF + 
                                vqi_pad_grninf_preop$hypermed)/5
  label(vqi_pad_grninf_preop$mFI) <- "Modified Frailty Index"

# ASA Class - Wiseman

  ##Create variables for ASA class 4 or for ASA class 5. Can utilize asaclas variable. - Wiseman
  vqi_pad_grninf_preop$asa_class_3 <-ifelse(vqi_pad_grninf_preop$ASACLASS == "3", TRUE, FALSE)
  label(vqi_pad_grninf_preop$asa_class_3) <- "ASA Class 3"

  vqi_pad_grninf_preop$asa_class_45 <-ifelse(vqi_pad_grninf_preop$ASACLASS == "4"| 
                                             vqi_pad_grninf_preop$ASACLASS == "5", TRUE, FALSE)
  label(vqi_pad_grninf_preop$asa_class_45) <- "ASA Class 4 or 5"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("ASACLASS"))]

# Dyspnea, bleeding disorder, and weightloss are not available in the VQI data set. - Wiseman

col_w_cormorbid <- colnames(vqi_pad_grninf_preop)
comorbid_col <- setdiff(col_w_cormorbid, col_no_comorbid)

table_2outcome(vqi_pad_grninf_preop, comorbid_col, "grninf", "s_grninf")

```

## Procedure Specific Variables

```{r Procedure Specific Variables, echo=FALSE, warning=FALSE, message=FALSE}

col_no_proc <- colnames(vqi_pad_grninf_preop)

# Indication - Leekha, Wiseman, Kalish, Eslami (mFI), Leekha

  ##Define variable for CLTI. - Leekha

  vqi_pad_grninf_preop$clti <-  
    ifelse(((vqi_pad_grninf_preop$SIDE == "Right" | 
             vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
             vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$R_INDICATIONR == "Rest Pain") |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$R_INDICATIONR == "Tissue Loss") |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$R_INDICATIONL == "Rest Pain") |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$R_INDICATIONL == "Tissue Loss") |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_R == "Rest Pain") |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_R == "Ulcer/necrosis") |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_R == "Non-healing amputation") |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_R == "Both ulcer and non-healing amp") |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_L == "Rest Pain") |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_L == "Ulcer/necrosis") |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_L == "Non-healing amputation") |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$INDICATION_OCCLUSIVE_L == "Both ulcer and non-healing amp"),
         TRUE, FALSE)
  vqi_pad_grninf_preop$clti <- replace(vqi_pad_grninf_preop$clti, is.na(vqi_pad_grninf_preop$clti), FALSE)
  label(vqi_pad_grninf_preop$clti) <- "Chronic Limb Threatening Ischemia"

# ABI Measurement - Kalish

  vqi_pad_grninf_preop$abi_35 <- 
    ifelse((vqi_pad_grninf_preop$PREOP_ABIR < 0.35) |
           (vqi_pad_grninf_preop$PREOP_ABIL < 0.35), TRUE, FALSE)
  vqi_pad_grninf_preop$abi_35[is.na(vqi_pad_grninf_preop$abi_35)] <- FALSE
  label(vqi_pad_grninf_preop$abi_35) <- "ABI <0.35"

## Active infection at time of procedure - Xu

  ##Xu utilizes WBC >9.9 at the time of procedure, which is likely a proxy for active infection at the time of
  ##Revascularization - Another proxy is the use of prolonged antibiotics, therefore we will use that instead.
  
  vqi_pad_grninf_preop$prolong_abx <-
    ifelse(vqi_pad_grninf_preop$ABX_STOP == "No" |
           vqi_pad_grninf_preop$ABX_STOP == "No, for medical reason" |
           vqi_pad_grninf_preop$R_ANTIBIOTICEND == "No" |
           vqi_pad_grninf_preop$R_ANTIBIOTICEND == "No, for medical reason", 
         TRUE, FALSE)
  vqi_pad_grninf_preop$prolong_abx <- replace(vqi_pad_grninf_preop$prolong_abx, list =
                                                    is.na(vqi_pad_grninf_preop$prolong_abx), FALSE)

# Prior ipsilateral Revascularization or Groin Incision - Leekha, Bennett, Fischer

  ## Bennett et al defined reoperative groin as "presence of previous groin incision on ipsilateral side." 
  ## We will use the variable for preivous bypass. - Bennett, Fischer
  vqi_pad_grninf_preop$reop_groin <- 
  ifelse(((vqi_pad_grninf_preop$SIDE == "Right" | 
             vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
             vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right")  & vqi_pad_grninf_preop$PINBYPASSR == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$PINBYPASSL == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right")  & vqi_pad_grninf_preop$PLEGBYPASSR == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$PLEGBYPASSL == TRUE),
         TRUE, FALSE)
  vqi_pad_grninf_preop$reop_groin <- ifelse(is.na(vqi_pad_grninf_preop$reop_groin), 
                                          FALSE, vqi_pad_grninf_preop$reop_groin)
  label(vqi_pad_grninf_preop$reop_groin) <- "Reoperative Groin"

 
  
  ## Leekha et al defines prior revascularization as either a prior surgical or 
  ##percutaneous revascularization procedure. We will not use R_PTASTENT or R_PRIOR_BYPASS.  
  ##Because we want to be sure the intervention was ipsilateral to the side of current intervention. 
  ##R_PRIOR_BYPASS is a retired variable representing a history of any non-coronary bypass.  
  ##This likely has significant overlap with this feature and so we will just remove this variable.
  ## Also used in Aziz.

  vqi_pad_grninf_preop$prrevasc_ips <- 
    ifelse(((vqi_pad_grninf_preop$SIDE == "Right" | 
             vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
             vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$PINBYPASSR == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$PINBYPASSL == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$PINPTASTENTR == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$PINPTASTENTL == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$PLEGBYPASSR == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$PLEGBYPASSL == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Right" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Right" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Right") & vqi_pad_grninf_preop$PLEGPTASTENTR == TRUE) |
           ((vqi_pad_grninf_preop$SIDE == "Left" | 
               vqi_pad_grninf_preop$GRFT_RECP1_SIDE == "Left" |
               vqi_pad_grninf_preop$GRFT_RECP2_SIDE == "Left") & vqi_pad_grninf_preop$PLEGPTASTENTL == TRUE)
         , TRUE, FALSE)
  vqi_pad_grninf_preop$prrevasc_ips <- ifelse(is.na(vqi_pad_grninf_preop$prrevasc_ips), 
                                            FALSE, vqi_pad_grninf_preop$prrevasc_ips)
  label(vqi_pad_grninf_preop$prrevasc_ips) <- "Prior Ipsilateral Revascularization"

## Previous Surgical Site Infection - Leekha - Not inlcuded in the VQI Data

## Combined Femoral Reconstruction - Xu
  
  vqi_pad_grninf_preop$endart <- ifelse(vqi_pad_grninf_preop$R_CCENDAR == TRUE |
                                          vqi_pad_grninf_preop$CC_IPS_ENDAR == "Inflow" |
                                          vqi_pad_grninf_preop$CC_IPS_ENDAR == "Outflow" |
                                          vqi_pad_grninf_preop$CC_IPS_ENDAR == "Both", TRUE, FALSE)
  vqi_pad_grninf_preop$endart <- ifelse(is.na(vqi_pad_grninf_preop$endart), 
                                        FALSE, vqi_pad_grninf_preop$endart)
  label(vqi_pad_grninf_preop$endart) <- "Combined Endarterectomy"

# Conduit Selection - Gwilym, Gwilym - Deep, Bennett, Fischer

  ## Create variable for vein bypass material - Gwilym

  vqi_pad_grninf_preop$vein <- ifelse(vqi_pad_grninf_preop$GRFTVTYPE == "Reversed GSV" |
                                      vqi_pad_grninf_preop$GRFTVTYPE == "In Situ GSV" |
                                      vqi_pad_grninf_preop$GRFTVTYPE == "Non-reversed Transposed GSV" |
                                      vqi_pad_grninf_preop$GRFTVTYPE == "Lesser Saph" |
                                      vqi_pad_grninf_preop$GRFTVTYPE == "Cephalic" |
                                      vqi_pad_grninf_preop$GRFTVTYPE == "Basilic" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "Reversed GSV" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "In Situ GSV" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "Non-reversed Transposed GSV" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "Lesser Saph" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "Cephalic" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "Basilic" |
                                      vqi_pad_grninf_preop$R_GRAFTVEINTYPE == "Composite Vein" |
                                      vqi_pad_grninf_preop$GRFT_RECP1_GRFT_TYPE == "Saphenous Vein" |
                                      vqi_pad_grninf_preop$GRFT_RECP1_GRFT_TYPE == "Deep Vein" |
                                      vqi_pad_grninf_preop$GRFT_RECP1_GRFT_TYPE == "Spliced Vein" |
                                      vqi_pad_grninf_preop$GRFT_RECP2_GRFT_TYPE == "Saphenous Vein" |
                                      vqi_pad_grninf_preop$GRFT_RECP2_GRFT_TYPE == "Deep Vein" |
                                      vqi_pad_grninf_preop$GRFT_RECP2_GRFT_TYPE == "Spliced Vein", TRUE, FALSE)
  vqi_pad_grninf_preop$vein <- replace(vqi_pad_grninf_preop$vein, is.na(vqi_pad_grninf_preop$vein), FALSE)
  label(vqi_pad_grninf_preop$vein) <- "Vein Conduit"

  ## Create variable for xenograft material - no exact variable for xenograft, so we will not be able to use.

  ## Create variable for prosthetic material - Gwilym, Gwilym - Deep, Fischer

  vqi_pad_grninf_preop$prsth <- ifelse(vqi_pad_grninf_preop$PROSTHETIC == "Dacron" |
                                       vqi_pad_grninf_preop$PROSTHETIC == "PTFE" |
                                       vqi_pad_grninf_preop$PROSTHETIC == "Other" |
                                       vqi_pad_grninf_preop$R_PROSTHETIC == "Dacron" |
                                       vqi_pad_grninf_preop$R_PROSTHETIC == "PTFE" |
                                       vqi_pad_grninf_preop$R_PROSTHETIC == "Composite w/ vein" |
                                       vqi_pad_grninf_preop$GRFT_RECP1_GRFT_TYPE == "Dacron" |
                                       vqi_pad_grninf_preop$GRFT_RECP1_GRFT_TYPE == "PTFE" |
                                       vqi_pad_grninf_preop$GRFT_RECP1_GRFT_TYPE == "Composite Prosthetic-vein" |
                                       vqi_pad_grninf_preop$GRFT_RECP2_GRFT_TYPE == "Dacron" |
                                       vqi_pad_grninf_preop$GRFT_RECP2_GRFT_TYPE == "PTFE" |
                                       vqi_pad_grninf_preop$GRFT_RECP2_GRFT_TYPE == "Composite Prosthetic-vein",
                                     TRUE, FALSE)
  vqi_pad_grninf_preop$prsth <- replace(vqi_pad_grninf_preop$prsth, is.na(vqi_pad_grninf_preop$prsth), FALSE)
  label(vqi_pad_grninf_preop$prsth) <- "Prosthetic Conduit"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("GRFTVTYPE", "R_GRAFTVEINTYPE", "PROSTHETIC", "R_PROSTHETIC", "GRFT_RECP1_GRFT_TYPE", "GRFT_RECP2_GRFT_TYPE"))]

# Operation Duration - Sorour, Wiseman, Gwilym, Aziz, Kalish, Xu

  ## Gwilym included optime as a continuous variable by hours. 
  ## Create variable for Procedure time in Hours and remove cases less than 0.5hrs and greater than 12 hours.

  vqi_pad_grninf_preop$optime_hrs <- ((vqi_pad_grninf_preop$TOTALPROCTIME)/60)

  vqi_pad_grninf_preop$optime_hrs[vqi_pad_grninf_preop$optime_hrs < 0.5] <- NA
  vqi_pad_grninf_preop$optime_hrs[vqi_pad_grninf_preop$optime_hrs > 12] <- NA

  ##Utilize optime variable and optime6h already created for Gwilym et al, 
  ##but create variable for optime between 4-6hr - Wiseman
  vqi_pad_grninf_preop$optime46h <- ifelse(vqi_pad_grninf_preop$optime_hrs > "4" & 
                                           vqi_pad_grninf_preop$optime_hrs < "6", TRUE, FALSE)
  label(vqi_pad_grninf_preop$optime46h) <- "Procedure Time 4-6 hours"
  
  ## Operative Length greater than 6 hours - Xu
  vqi_pad_grninf_preop$optime6h <- ifelse(vqi_pad_grninf_preop$optime_hrs > "6", TRUE, FALSE)
  label(vqi_pad_grninf_preop$optime6h) <- "Procedure Time > 6 hours"

  ##Create variable for operative time> 220 minutes - Kalish
  vqi_pad_grninf_preop$optime220 <- ifelse(vqi_pad_grninf_preop$TOTALPROCTIME >"220", TRUE, FALSE)
  vqi_pad_grninf_preop$optime220 <- ifelse(is.na(vqi_pad_grninf_preop$optime220), 
                                         FALSE, vqi_pad_grninf_preop$optime220)
  label(vqi_pad_grninf_preop$optime220) <- "Procedure Time >220 Minutes"
  
  ##Operative Duration >5hrs - Sorour, same as >300min - Aziz
  vqi_pad_grninf_preop$optime5h <- ifelse(vqi_pad_grninf_preop$optime_hrs > "5", TRUE, FALSE)
  vqi_pad_grninf_preop$optime5h <- ifelse(is.na(vqi_pad_grninf_preop$optime5h), 
                                        FALSE, vqi_pad_grninf_preop$optime5h)
  label(vqi_pad_grninf_preop$optime5h) <- "Procedure Time > 5 Hours"

# Procedure Urgency - Bennett

  ## Bennett uses urgency, we will use URGENCY variable - Bennett
  vqi_pad_grninf_preop$urgnt <- ifelse(vqi_pad_grninf_preop$URGENCY == "Urgent" |
                                       vqi_pad_grninf_preop$URGENCY == "Emergent", TRUE, FALSE)
  label(vqi_pad_grninf_preop$urgnt) <- "Urgent or Emergent Procedure"

  ##Create emergent variable - Wiseman
  vqi_pad_grninf_preop$emrgnt <-ifelse(vqi_pad_grninf_preop$URGENCY == "Emergent", TRUE, FALSE)
  label(vqi_pad_grninf_preop$emrgnt) <- "Emergent Procedure"

  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("URGENCY"))]

# Skin Preparation Type - Gwilym

  ## Create variable Skin_preparation.  VQI includes this as a variable SKINPREP.  "Alcohol" was not mentioned
  ## in the Gwilym article so this was not mapped

  vqi_pad_grninf_preop$SKINPREP <- fct_explicit_na(vqi_pad_grninf_preop$SKINPREP, na_level = "Unknown")

  vqi_pad_grninf_preop$prep_al_chlo <- ifelse(vqi_pad_grninf_preop$SKINPREP == "Chlor + alcohol", TRUE, FALSE)
  label(vqi_pad_grninf_preop$prep_al_chlo) <- "Prep with Alcoholic Chlorhexidine"
  vqi_pad_grninf_preop$prep_aq_chlo <- ifelse(vqi_pad_grninf_preop$SKINPREP == "Chlorhexidine", TRUE, FALSE)
  label(vqi_pad_grninf_preop$prep_aq_chlo) <- "Prep with Aqueous Chlorhexidine"
  vqi_pad_grninf_preop$prep_al_beta <- ifelse(vqi_pad_grninf_preop$SKINPREP == "Iodine + alcohol", TRUE, FALSE)
  label(vqi_pad_grninf_preop$prep_al_beta) <- "Prep with Iodine and Alcohol"
  vqi_pad_grninf_preop$prep_aq_beta <- ifelse(vqi_pad_grninf_preop$SKINPREP == "Iodine", TRUE, FALSE)
  label(vqi_pad_grninf_preop$prep_aq_beta) <- "Prep with Aqeuous Iodine"
  vqi_pad_grninf_preop$prep_two_thr <- ifelse(vqi_pad_grninf_preop$SKINPREP == "Chlor + iodine" |
                                              vqi_pad_grninf_preop$SKINPREP == "All 3", TRUE, FALSE)
  label(vqi_pad_grninf_preop$prep_two_thr) <- "Prep with Two or Three Solutions"
  vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("SKINPREP"))]


  ## Chlorhexidine was found to be protective. 
  ## We will use the same variable created for chlorhexidine with and without alcohol - Kalish
  vqi_pad_grninf_preop$prep_any_chlo <- ifelse(vqi_pad_grninf_preop$prep_aq_chlo == TRUE |
                                               vqi_pad_grninf_preop$prep_al_chlo == TRUE, TRUE, FALSE)
  vqi_pad_grninf_preop$prep_any_chlo[is.na(vqi_pad_grninf_preop$prep_any_chlo)] <- FALSE
  label(vqi_pad_grninf_preop$prep_any_chlo) <- "Prep with Chlorhexidine w/ or w/o Alcohol"


#Post operative variables - excluded from performance evaluation

  ## Reoperation - Wiseman, Aziz
  ## Wound disruption/dehiscence - Aziz
  ## Postoperative Blood Transfusion - Wiseman, Aziz, Kalish
  ## Prolonged length of stay (>28d) - Aziz
  ## Postoperative UTI - Aziz

col_w_proc <- colnames(vqi_pad_grninf_preop)
proc_col <- setdiff(col_w_proc, col_no_proc)

print(proc_col)

table_2outcome(vqi_pad_grninf_preop, proc_col, "grninf", "s_grninf")

```

# Discrimination and Calbiration

We performed validation for discrimination and calibration. We performed an ROC Curve and calculated AUC to determine discrimination. We performed a calibration plot to determine calibration. When the full regression model was available, inclusive of the intercept, this was used for validation of both discrimination and calibration. When no intercept was included, then the beta-coefficients or odds ratios were used only for validation of discrimination. In these cases where a clinical nomogram was provided, this was used to validate calibration.

```{r calculate prediction and nomogram values, warning=FALSE, message=FALSE, echo=FALSE}

attach(vqi_pad_grninf_preop)

# Calculate predicted values for Gwilym et al
vqi_pad_grninf_preop$g_beta <- -4.846 +
         0.535*(female) +
         0.629*(underweight) +
         0.264*(overweight) +
         1.070*(obese) +
         0.793*(heart_dz) -
         0.394*(prep_aq_chlo) -
         0.058*(prep_al_beta) +
         1.024*(prep_aq_beta) +
         0.021*(prep_two_thr) +
         0.884*(vein) +
         0.938*(prsth) +
         0.142*(optime_hrs)
vqi_pad_grninf_preop$g_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$g_beta))

#Calculate predicted values for Gwilym et al deep SSI model
vqi_pad_grninf_preop$gd_beta <- -4.262 +
         0.666*(female) +
         0.666*(dm_any) -
         0.108*(prep_aq_chlo) -
         0.332*(prep_al_beta) +
         1.418*(prep_aq_beta) +
         0.207*(prep_two_thr) +
         0.027*(vein) +
         0.325*(prsth)
vqi_pad_grninf_preop$gd_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$gd_beta))

#Calculate predicted values for Leekha et al
vqi_pad_grninf_preop$l_beta <- 1.07*(clti) +
          0.74*(hxcopd) +
          0.99*(prrevasc_ips)
vqi_pad_grninf_preop$l_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$l_beta))

vqi_pad_grninf_preop$l_score <-
  1*clti +
  1*hxcopd +
  1*prrevasc_ips +
  2*(0)

vqi_pad_grninf_preop$l_nomo <- case_when(
  vqi_pad_grninf_preop$l_score == 0 ~ 0.01,
  vqi_pad_grninf_preop$l_score == 1 ~ 0.03,
  vqi_pad_grninf_preop$l_score == 2 ~ 0.06,
  vqi_pad_grninf_preop$l_score == 3 ~ 0.12,
  vqi_pad_grninf_preop$l_score == 4 ~ 0.28,
  vqi_pad_grninf_preop$l_score == 5 ~ 0.49
)

#Calculate predicted values for Bennett et al
vqi_pad_grninf_preop$b_beta <- log(3.01)*(reop_groin) +
             log(3.46)*(female) +
             log(1.01)*(BMI) +
             log(4.37)*(esrd) +
             log(7.22)*(malnut) +
             log(2.98)*(urgnt)
vqi_pad_grninf_preop$b_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$b_beta))

#Calculate predicted values for Wiseman et al 
vqi_pad_grninf_preop$w_beta <- log(1.4)*(female) +
                log(0.9)*(age65) +
                log(0.8)*(blkrace) +
                log(0.9)*(othrace) +
                log(1.3)*(overweight) +
                log(2.3)*(obese) +
                log(0.8)*(underweight) +
                log(1.3)*(dm_ins) + 
                log(1.2)*(dm_nonins) +
                log(1.2)*(smoke) +
                log(1.2)*(hypermed) +
                log(1.1)*(heart_dz) +
                log(1.2)*(clti) +
                log(1.1)*(fnst_par) +
                log(0.5)*(fnst_dep) +
                log(1.1)*(hxcopd) +
                log(1.1)*(neuro) +
                log(1.4)*(optime46h) +
                log(1.5)*(optime6h) +
                log(2.4)*(proc_ai) +
                log(3.1)*(proc_ler) +
                log(1.2) +
                log(0.9)*(vein) +
                log(0.8)*(prsth) +
                log(1.1)*(asa_class_3) +
                log(1.2)*(asa_class_45)
vqi_pad_grninf_preop$w_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$w_beta)) 

vqi_pad_grninf_preop$w_score <-
  12*proc_ler +
  9*proc_ai +
  9*obese +
  5*optime6h +
  4*female +
  3*overweight +
  3*optime46h +
  3*dm_ins +
  2*dm_nonins +
  2*smoke +
  2*hypermed +
  2*clti +
  2*(0) + #dyspnea with moderate exercise
  2*(1) + #groin anastomosis
  2*asa_class_45 +
  1*hxcopd +
  1*heart_dz +
  1*neuro -
  1*age65 -
  2*blkrace -
  4*(0) - #sepsis complication
  6*(0) - #renal complication
  6*fnst_dep -
  9*(0) #LOS >14d

vqi_pad_grninf_preop$w_nomo <- case_when(
  vqi_pad_grninf_preop$w_score < 16 ~ 0.021,
  vqi_pad_grninf_preop$w_score >= 16 & vqi_pad_grninf_preop$w_score <= 20 ~ 0.051,
  vqi_pad_grninf_preop$w_score >= 21 & vqi_pad_grninf_preop$w_score <= 25 ~ 0.078,
  vqi_pad_grninf_preop$w_score >25 ~ 0.14
)

vqi_pad_grninf_preop$s_score <- obese + dm_ins + hxcopd + optime5h

vqi_pad_grninf_preop$s_nomo <- case_when(
  vqi_pad_grninf_preop$s_score == 0 ~ 0.12,
  vqi_pad_grninf_preop$s_score == 1 ~ 0.10,
  vqi_pad_grninf_preop$s_score == 2 ~ 0.12,
  vqi_pad_grninf_preop$s_score == 3 ~ 0.43,
  vqi_pad_grninf_preop$s_score == 4 ~ 0.6,
  vqi_pad_grninf_preop$s_score == 5 ~ 1.0
)

#Calculate predicted values for Eslami et al 
vqi_pad_grninf_preop$mFI <- as.numeric(vqi_pad_grninf_preop$mFI)

vqi_pad_grninf_preop$e_beta <- log(1.01)*(mFI) +
                log(0.98)*(AGE) +
                log(1.3)*(female) +
                log(1.44)*(overweight) +
                log(2.73)*(obese) +
                log(0.86)*(cr_152) +
                log(1.33)*(cr_gr2) +
                log(1.08)*(asa_class_3) + 
                log(1.86)*(asa_class_45)
vqi_pad_grninf_preop$e_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$e_beta))

#Calculate predicted values for Aziz et al 
vqi_pad_grninf_preop$a_beta <- log(2.28)*(BMI40) +
  log(1.98)*(optime5h) +
  log(1.98)*(prrevasc_ips) +
  log(1.73)*(hxcopd)
vqi_pad_grninf_preop$a_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$a_beta))

#Calculate predicted values for Kalish et al 
vqi_pad_grninf_preop$k_beta <- 
  log(1.54)*(abi_35) +
  log(2.11)*(optime220) +
  log(0.53)*(prep_any_chlo)
vqi_pad_grninf_preop$k_pred <- 1 / (1+exp(-vqi_pad_grninf_preop$k_beta))

vqi_pad_grninf_preop$k_score <- abi_35 + optime220 + prep_any_chlo

vqi_pad_grninf_preop$k_nomo <- case_when(
  vqi_pad_grninf_preop$k_score == 0 ~ 0,
  vqi_pad_grninf_preop$k_score == 1 ~ 0.032,
  vqi_pad_grninf_preop$k_score == 2 ~ 0.048,
  vqi_pad_grninf_preop$k_score == 3 ~ 0.102
)

vqi_pad_grninf_preop$x_score <- 4 * BMI35 + 2 * whtrace + 2 * endart + no_heart_dz + age73 + dm_any +
  optime6h + prolong_abx

vqi_pad_grninf_preop$x_nomo <- case_when(
  vqi_pad_grninf_preop$x_score <= 3 ~ 0.045,
  (vqi_pad_grninf_preop$x_score >= 4 &
     vqi_pad_grninf_preop$x_score <=7) ~ 0.085,
  (vqi_pad_grninf_preop$x_score >= 8 &
     vqi_pad_grninf_preop$x_score <= 11) ~ 0.138,
  vqi_pad_grninf_preop$x_score >= 12 ~ 0.238
)

vqi_pad_grninf_preop$f_score <- 2 * obese + 2 * smoke + 2 * reop_groin + prsth

vqi_pad_grninf_preop$f_nomo <- case_when(
  vqi_pad_grninf_preop$f_score <= 2 ~ 0.202,
  (vqi_pad_grninf_preop$f_score >= 3 &
     vqi_pad_grninf_preop$f_score <= 4) ~ 0.50,
  vqi_pad_grninf_preop$f_score >= 5 ~ 0.71
)


vqi_pad_grninf_preop <- vqi_pad_grninf_preop[ , !(names(vqi_pad_grninf_preop) %in% c("g_beta", "gd_beta", "l_beta", "b_beta", "w_beta", 
                                                                                     "l_score", "w_score", "s_score", "e_beta", 
                                                                                     "a_beta", "k_beta", "k_score", "x_score", 
                                                                                     "f_score"))]

models_disc <- tibble(
  Labels = c("Aziz", "Bennett", "Eslami", "Fischer", "Gwilym", "Gwilym - Deep", "Kalish", "Leehka", "Sorour", "Wiseman", "Xu"),
  Prediction = c("a_pred", "b_pred", "e_pred", "f_nomo", "g_pred", "gd_pred", "k_nomo", "l_nomo", "s_nomo", "w_nomo", "x_nomo")
)


models_cal <- tibble(
  Labels = c("Fischer", "Gwilym", "Gwilym - Deep", "Kalish", "Leehka", "Sorour", "Wiseman", "Xu"),
  Prediction = c("f_nomo", "g_pred", "gd_pred", "k_nomo", "l_nomo", "s_nomo", "w_nomo", "x_nomo")
)

```

## Discrimination for Any Groin SSI

```{r ROC Curves for grninf, warning=FALSE, message=FALSE, echo=FALSE}

vqi_pad_grninf_preop$grninf <- as.factor(vqi_pad_grninf_preop$grninf)

plot_auc(models_disc, vqi_pad_grninf_preop, "grninf", "AUC for Any Groin Infection - VQI")

```

## Discriminiation for Severe Groin SSI

```{r ROC Curves for s_grninf, warning=FALSE, message=FALSE, echo=FALSE}

vqi_pad_grninf_preop$s_grninf <- as.factor(vqi_pad_grninf_preop$s_grninf)

plot_auc(models_disc, vqi_pad_grninf_preop, "s_grninf", "AUC for Severe Groin Infection - VQI")

```

## Calibration for Any Groin SSI

```{r calibration plots for any groin SSI, warning=FALSE, message=FALSE, echo=FALSE}

plot_calibration(models_cal, vqi_pad_grninf_preop, "grninf", "Any Groin Infection - VQI")

```

```{r ece for any groin SSI, echo=FALSE, message=FALSE, warning=FALSE}

# Convert grninf to numeric (0/1)
vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
  mutate(outcome_num = as.numeric(as.logical(grninf)))

# Initialize results list
ece_results <- list()

# Loop through each model
for (model_name in models_cal$Prediction) {
  
  # Filter out rows with missing predictions or outcome
  df <- vqi_pad_grninf_preop[!is.na(vqi_pad_grninf_preop[[model_name]]) & !is.na(vqi_pad_grninf_preop$outcome_num), ]
  
  # Calculate mean ece
  pred <- df[[model_name]]
  truth <- df$outcome_num
  mean_ece <- calc_ece(pred, truth)
  
  # Bootstrap
  boot_out <- boot(data = df, statistic = function(data, i) boot_ece(data, i, model_name), R = 200, parallel = "snow")

  ci <- boot.ci(boot_out, type = "perc", index = 1)

  # Store results
  ece_results[[model_name]] <- list(
    Model = model_name,
    ece = mean_ece,
    ci_lower = ci$percent[4],
    ci_upper = ci$percent[5],
    n = nrow(df)  # Optional: include sample size used
  )
}

ece_grninf <- bind_rows(ece_results)

ece_grninf <- ece_grninf %>%
    left_join(models_cal, by = c("Model" = "Prediction")) %>%
    select(Labels, Model, ece, ci_lower, ci_upper)

print(ece_grninf)

# Create the forest plot
  ggplot(ece_grninf, aes(x = ece, y = reorder(Labels, 1/ece))) +
    geom_point(size = 1, color = "black") +
    geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0.2, color = "gray30") +
    theme_bw(base_size = 12) +
    xlim(0,0.275) +
    labs(x = "ECE (95% CI)", y = "", title = paste("ECE for Any Groin Infection - VQI")) +
    theme(panel.grid.major.y = element_blank())

```



## Calibration for Severe Groin SSI

```{r calibration plots for severe groin SSI, warning=FALSE, message=FALSE, echo=FALSE}

plot_calibration(models_cal, vqi_pad_grninf_preop, "s_grninf", "Severe Groin Infection - VQI")

```

```{r ECE for severe groin SSI, warning=FALSE, message=FALSE, echo=FALSE}

# Convert grninf to numeric (0/1)
vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
  mutate(outcome_num = as.numeric(as.logical(s_grninf)))

# Initialize results list
ece_results <- list()

# Loop through each model
for (model_name in models_cal$Prediction) {
  
  # Filter out rows with missing predictions or outcome
  df <- vqi_pad_grninf_preop[!is.na(vqi_pad_grninf_preop[[model_name]]) & !is.na(vqi_pad_grninf_preop$outcome_num), ]
  
  # Calculate mean ece
  pred <- df[[model_name]]
  truth <- df$outcome_num
  mean_ece <- calc_ece(pred, truth)
  
  # Bootstrap
  boot_out <- boot(data = df, statistic = function(data, i) boot_ece(data, i, model_name), R = 200, parallel = "snow")

  ci <- boot.ci(boot_out, type = "perc", index = 1)

  # Store results
  ece_results[[model_name]] <- list(
    Model = model_name,
    ece = mean_ece,
    ci_lower = ci$percent[4],
    ci_upper = ci$percent[5],
    n = nrow(df)  # Optional: include sample size used
  )
}

ece_s_grninf <- bind_rows(ece_results)

ece_s_grninf <- ece_s_grninf %>%
    left_join(models_cal, by = c("Model" = "Prediction")) %>%
    select(Labels, Model, ece, ci_lower, ci_upper)

print(ece_s_grninf)

# Create the forest plot
  ggplot(ece_s_grninf, aes(x = ece, y = reorder(Labels, 1/ece))) +
    geom_point(size = 1, color = "black") +
    geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0.2, color = "gray30") +
    theme_bw(base_size = 12) +
    labs(x = "ECE (95% CI)", y = "", title = paste("ECE for Severe Groin Infection - VQI")) +
    theme(panel.grid.major.y = element_blank())
  
```
# Bias Assessment

```{r bias assessment, warning=FALSE, message=FALSE, echo=FALSE}

bias_vars <- c("female", "blkrace", "SURGYEAR", "indication", "proc", "prsth")

## Use ECE, not log-loss or no BSS because this is a rare event

df <- vqi_pad_grninf_preop %>%
    filter(!is.na(female) & !is.na(blkrace))

# Convert grninf to numeric (0/1)
vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
  mutate(outcome_num = as.numeric(as.logical(grninf)))

# Initialize results list
biasll_results <- list()

for (subgroup_var in bias_vars) {
  #Remove NA levels of bias variables

  subgroup_data <- df %>%
    group_by(.data[[subgroup_var]]) %>%
    group_split()
  
  for (group in subgroup_data) {
    group_name <- unique(group[[subgroup_var]])
    
    for (model_name in models_cal$Prediction) {
  
      # Filter out rows with missing predictions or outcome
      df <- vqi_pad_grninf_preop[!is.na(vqi_pad_grninf_preop[[model_name]]) & !is.na(vqi_pad_grninf_preop$outcome_num), ]
  
      # Calculate mean ece
      pred <- df[[model_name]]
      truth <- df$outcome_num
      mean_ece <- calc_ece(pred, truth)
  
      # Bootstrap
      boot_out <- boot(data = df, statistic = function(data, i) boot_ece(data, i, model_name), R = 200, parallel = "snow")

      ci <- boot.ci(boot_out, type = "perc", index = 1)
      
      # Convert logical to factor with levels "TRUE" and "FALSE"
      group_name_clean <- group_name

      if (is.logical(group_name_clean)) {
         group_name_clean <- factor(group_name_clean, levels = c(TRUE, FALSE))
          }

      biasll_results[[length(biasll_results) + 1]] <- tibble(
        Subgroup_Var = subgroup_var,
        Subgroup_Level = group_name_clean,
        Model = model_name,
        mean = mean(boot_out$t),
        ci_lower = ci$percent[4],
        ci_upper = ci$percent[5],
        n = nrow(df)
      )
    }
  }
}

biasll_df <- bind_rows(biasll_results)

# Get unique model names
model_list <- unique(biasll_df$Model)

# Create a named list of plots
plot_list <- map(model_list, function(model_name) {
  
  # Subset data for the current model
  subset_df <- biasll_df %>%
    filter(Model == model_name) %>%
    mutate(Subgroup_Combined = paste(Subgroup_Var, Subgroup_Level, sep = ":"))
  
  # Set a value for reference line
  ref_line_value <- ece_grninf %>%
    filter(Model == model_name) %>%
    pull(ece)

  # Create the forest plot
  ggplot(subset_df, aes(x = mean, y = Subgroup_Combined)) +
    geom_point(size = 1, color = "black") +
    geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0.2, color = "gray30") +
    theme_bw(base_size = 12) +
    geom_vline(xintercept = ref_line_value, linetype = "dashed", color = "black") +
    xlim(0,0.275) +
    labs(x = "ECE (95% CI)", y = "", title = paste("Forest Plot of ECE -", model_name)) +
    theme(panel.grid.major.y = element_blank())
})

# Optionally name the list for easy reference
# names(plot_list) <- model_list

# Example: display plot for "x_nomo"
print(plot_list)

```


```{r export data, echo=FALSE, warning=FALSE, message=FALSE}

vqi_pad_grninf_preop$grninf <- as.logical(vqi_pad_grninf_preop$grninf)
vqi_pad_grninf_preop$s_grninf <- as.logical(vqi_pad_grninf_preop$s_grninf)

#ff_glimpse(vqi_pad_grninf_preop)

saveRDS(vqi_pad_grninf_preop, file="../../DataRepo/VQI/Analysis Data Files/vqi_pad_grninf_preop.rds")

```

```{r OLD CODE, eval=FALSE, echo=FALSE}
g_df <- vqi_pad_grninf_preop[, c(g_exp, "grninf"), drop = FALSE]
g_df <- g_df[complete.cases(g_df),]

g_beta_coefficients <- c(
  Intercept = -4.846,
  female = 0.535,
  underweight = 0.629,
  overweight = 0.264,
  obese = 1.070,
  heart_dz = 0.793,
  prep_aq_chlo = -0.394,
  prep_al_beta = -0.058,
  prep_aq_beta = 1.024,
  prep_two_thr = 0.021,
  vein = 0.884,
  prsth = 0.938,
  optime_hrs = 0.142
)

## Create the model matrix
g_joined <- paste(g_exp, collapse = " + ")
g_formula <- as.formula(paste("~", g_joined))
model_matrix <- model.matrix(g_formula, data = g_df)

## Calculate the linear predictor (g_beta)
g_beta <- model_matrix %*% g_beta_coefficients

## Calculate the predicted values using the logistic function
g_df$.pred_TRUE <- 1 / (1 + exp(g_beta))

# Calculate predicted values for Leekha et al
l_df <- vqi_pad_grninf_preop[, c(l_exp, "grninf"), drop = FALSE]
l_df <- l_df[complete.cases(l_df),]

l_beta_coefficients <- c(
  Intercept = 0, #The intercept is unknown so we will use 0
  clti = 1.07,
  hxcopd = 0.74,
  prrevasc_ips = 0.99
)

## Create the model matrix
l_joined <- paste(l_exp, collapse = " + ")
l_formula <- as.formula(paste("~ ", l_joined))
model_matrix <- model.matrix(l_formula, data = l_df)

## Calculate the linear predictor (l_beta)
l_beta <- model_matrix %*% l_beta_coefficients

## Calculate the predicted values using the logistic function
l_df$l_pred <- 1 / (1 + exp(l_beta))


b_df <- vqi_pad_grninf_preop[, c(b_exp, "grninf"), drop = FALSE]
b_df <- b_df[complete.cases(b_df),]

b_beta_coefficients <- c(
  Intercept = 0, #The intercept is unknown so we will use 0
  reop_groin = log(3.01),
  female = log(3.46),
  BMI = log(1.01),
  esrd = log(4.37),
  malnut = log(7.22),
  urgnt = log(2.98)
)

## Create the model matrix
b_joined <- paste(b_exp, collapse = " + ")
b_formula <- as.formula(paste("~ ", b_joined))
model_matrix <- model.matrix(b_formula, data = b_df)

## Calculate the linear predictor (b_beta)
b_beta <- model_matrix %*% b_beta_coefficients

## Calculate the predicted values using the logistic function
b_df$b_pred <- 1 / (1 + exp(b_beta))

w_df <- vqi_pad_grninf_preop[, c(w_exp, "grninf"), drop = FALSE]
w_df <- w_df[complete.cases(w_df),]

w_beta_coefficients <- c(
  Intercept = log(1.2), #All patients have a groin anastomosis so we will include this term as the intercept, even though the intercept is not known
  female = log(1.4),
  age65 = log(0.9),
  blkrace = log(0.8),
  othrace = log(0.9),
  overweight = log(1.3),
  obese = log(2.3),
  underweight = log(1.3),
  dm_ins = log(1.3),
  dm_nonins = log(1.2),
  smoke = log(1.2),
  hypermed = log(1.2),
  heart_dz = log(1.1),
  clti = log(1.2),
  fnst_par = log(1.1),
  fnst_dep = log(0.5),
  hxcopd = log(1.1),
  neuro = log(1.1),
  optime46h = log(1.4),
  optime6h = log(1.5),
  proc_ai = log(2.4),
  proc_ler = log(3.1),
  vein = log(0.9),
  prsth = log(0.8),
  asa_class_3 = log(1.1),
  asa_class_45 = log(1.2)
)

## Create the model matrix
w_joined <- paste(w_exp, collapse = " + ")
w_formula <- as.formula(paste("~ ", w_joined))
model_matrix <- model.matrix(w_formula, data = w_df)

## Calculate the linear predictor (b_beta)
w_beta <- model_matrix %*% w_beta_coefficients

## Calculate the predicted values using the logistic function
w_df$w_pred <- 1 / (1 + exp(w_beta))

l_df$grninf <- as.logical(l_df$grninf)
l_df$grninf <- as.numeric(l_df$grninf)
calibration_plot(data = l_df, obs = "grninf", pred = "l_pred", title = "Calibration plot for Leekha et al", y_lim = c(0, 1), x_lim=c(0, 1))

b_df$grninf <- as.logical(b_df$grninf)
b_df$grninf <- as.numeric(b_df$grninf)
calibration_plot(data = b_df, obs = "grninf", pred = "b_pred", title = "Calibration plot for Bennett et al", y_lim = c(0, 0.7), x_lim=c(0, 0.7))

w_df$grninf <- as.logical(w_df$grninf)
w_df$grninf <- as.numeric(w_df$grninf)
calibration_plot(data = w_df, obs = "grninf", pred = "w_pred", title = "Calibration plot for Wiseman et al", y_lim = c(0, 1), x_lim=c(0, 1))

#General ROC curves - replaced with a loop
roc_g <- roc_curve(vqi_pad_grninf_preop, grninf, g_pred)
auc_g <- roc_auc(vqi_pad_grninf_preop, grninf, g_pred)
auc_g_round <- round(auc_g$.estimate, 2)

roc_gd <- roc_curve(vqi_pad_grninf_preop, grninf, gd_pred)
auc_gd <- roc_auc(vqi_pad_grninf_preop, grninf, gd_pred)
auc_gd_round <- round(auc_gd$.estimate, 2)

roc_l <- roc_curve(vqi_pad_grninf_preop, grninf, l_pred)
auc_l <- roc_auc(vqi_pad_grninf_preop, grninf, l_pred)
auc_l_round <- round(auc_l$.estimate, 2)

roc_ln <- roc_curve(vqi_pad_grninf_preop, grninf, l_nomo)
auc_ln <- roc_auc(vqi_pad_grninf_preop, grninf, l_nomo)
auc_ln_round <- round(auc_ln$.estimate, 2)

roc_b <- roc_curve(vqi_pad_grninf_preop, grninf, b_pred)
auc_b <- roc_auc(vqi_pad_grninf_preop, grninf, b_pred)
auc_b_round <- round(auc_b$.estimate, 2)

roc_w <- roc_curve(vqi_pad_grninf_preop, grninf, w_pred)
auc_w <- roc_auc(vqi_pad_grninf_preop, grninf, w_pred)
auc_w_round <- round(auc_w$.estimate, 2)

roc_wn <- roc_curve(vqi_pad_grninf_preop, grninf, w_nomo)
auc_wn <- roc_auc(vqi_pad_grninf_preop, grninf, w_nomo)
auc_wn_round <- round(auc_wn$.estimate, 2)

#w_df <- vqi_pad_grninf_preop[, c(w_exp, "grninf", "w_score", "w_nomo"), drop = FALSE]
#w_df <- w_df[complete.cases(w_df),]
#w_df$w_score <- as.numeric(w_df$w_score)

#summary(w_df$w_score)

#event_rate <- w_df %>%
#  group_by(w_score) %>%
#  summarise(rate = mean(grninf, na.rm = TRUE))

#exp <- c("w_score")

#w_df %>%
#  summary_factorlist(dependent, exp, p=TRUE, add_dependent_label=TRUE,
#                     add_col_totals = TRUE, column = FALSE,
#                     include_col_totals_percent = FALSE,
#                     col_totals_rowname = "",
#                     col_totals_prefix = "N=") -> w_t2
#knitr::kable(w_t2, align = c("l", "l", "r", "r", "r"))

#print(event_rate)
#roc <- roc_curve(w_df, grninf, w_score)
#autoplot(roc)

library(dplyr)

# Define Brier Score and Brier Skill Score functions
brier_score <- function(pred, truth) {
  mean((pred - truth)^2)
}

brier_skill_score <- function(pred, truth, ref_prob) {
  bs_model <- brier_score(pred, truth)
  bs_ref <- brier_score(rep(ref_prob, length(truth)), truth)
  1 - (bs_model / bs_ref)
}

# Reference probability (overall event rate)
vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
  mutate(grninf_num = as.numeric(grninf) - 1)  # assuming levels
ref_prob <- mean(vqi_pad_grninf_preop$grninf_num)

# Initialize empty list to store results
bss_results <- list()

# Loop over subgroup variables
for (subgroup_var in bias_vars) {
  
  subgroup_data <- vqi_pad_grninf_preop %>%
    group_by(.data[[subgroup_var]]) %>%
    group_split()
  
  for (group in subgroup_data) {
    group_name <- unique(group[[subgroup_var]])
    
    for (model_var in models_bias$Prediction) {
      
      pred <- group[[model_var]]
      truth <- group$grninf
      
      bss <- brier_skill_score(pred, truth, ref_prob)
      
      bss_results[[length(bss_results) + 1]] <- tibble(
        Subgroup_Var = subgroup_var,
        Subgroup_Level = group_name,
        Model = model_var,
        BSS = bss
      )
    }
  }
}




summary(vqi_pad_grninf_preop$grninf_num)


vqi_clean <- vqi_pad_grninf_preop %>%
  filter(!is.na(x_nomo), !is.na(grninf))

summary(vqi_clean$grninf)

# Calculate BSS by 'female' subgroup
bss_by_female <- vqi_clean %>%
  group_by(female) %>%
  summarise(
    BSS_x_nomo = brier_skill_score(x_nomo, grninf, ref_prob),
    .groups = "drop"
  )


# Combine results into a single dataframe
bss_df <- bind_rows(bss_results)

vqi_clean <- vqi_pad_grninf_preop %>%
  filter(!is.na(x_nomo), !is.na(grninf)) %>%
  mutate(grninf_num = as.numeric(grninf) - 1)

ref_prob <- mean(vqi_clean$grninf_num)

brier_score <- function(pred, truth) {
  mean((pred - truth)^2)
}

brier_skill_score <- function(pred, truth, ref_prob) {
  bs_model <- brier_score(pred, truth)
  bs_ref <- brier_score(rep(ref_prob, length(truth)), truth)
  if (bs_ref == 0) return(NA)  # avoid division by zero
  1 - (bs_model / bs_ref)
}

bss_by_female <- vqi_clean %>%
  group_by(female) %>%
  summarise(
    BSS_x_nomo = brier_skill_score(x_nomo, grninf_num, ref_prob),
    .groups = "drop"
  )


# Ensure grninf is numeric (0/1)
vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
  mutate(grninf_num = as.numeric(grninf))  # TRUE = 1, FALSE = 0

# Initialize results list
bss_results <- list()

# Loop through subgroup variables
for (subgroup_var in bias_vars) {
  
  # Split data by subgroup
  subgroup_data <- vqi_pad_grninf_preop %>%
    group_by(.data[[subgroup_var]]) %>%
    group_split()
  
  for (group in subgroup_data) {
    group_name <- unique(group[[subgroup_var]])
    
    for (model_var in models_cal$Prediction) {
      
      # Remove rows with missing predictions
      group_filtered <- group %>%
        filter(!is.na(.data[[model_var]]))
      
      # Skip if no rows remain
      if (nrow(group_filtered) == 0) next
      
      # Extract predictions and truth
      pred <- group_filtered[[model_var]]
      truth <- group_filtered$grninf_num
      
      # Compute BSS
      bss <- brier_skill_score(pred, truth, ref_prob)
      
      # Store result
      bss_results[[length(bss_results) + 1]] <- tibble(
        Subgroup_Var = subgroup_var,
        Subgroup_Level = group_name,
        Model = model_var,
        BSS = bss
      )
    }
  }
}

# Combine into a single dataframe
bss_df <- bind_rows(bss_results)


library(dplyr)
library(boot)

# Ensure grninf is numeric (0/1)
vqi_pad_grninf_preop <- vqi_pad_grninf_preop %>%
  mutate(grninf_num = as.numeric(grninf))  # TRUE = 1, FALSE = 0

# Brier Score and Brier Skill Score functions
brier_score <- function(pred, truth) {
  mean((pred - truth)^2)
}

brier_skill_score <- function(pred, truth, ref_prob) {
  bs_model <- brier_score(pred, truth)
  bs_ref <- brier_score(rep(ref_prob, length(truth)), truth)
  if (bs_ref == 0) return(NA)
  1 - (bs_model / bs_ref)
}

# Bootstrap function for BSS
bootstrap_bss <- function(data, indices, model_var, ref_prob) {
  d <- data[indices, ]
  pred <- d[[model_var]]
  truth <- d$grninf_num
  brier_skill_score(pred, truth, ref_prob)
}

# Reference probability
ref_prob <- mean(vqi_pad_grninf_preop$grninf_num)

# Initialize results list
bss_results <- list()



# Loop through subgroup variables
for (subgroup_var in bias_vars) {
  
  subgroup_data <- vqi_pad_grninf_preop %>%
    group_by(.data[[subgroup_var]]) %>%
    group_split()
  
  for (group in subgroup_data) {
    group_name <- unique(group[[subgroup_var]])
    
    for (model_var in models_cal$Prediction) {
      
      # Remove rows with missing predictions
      group_filtered <- group %>%
        filter(!is.na(.data[[model_var]]))
      
      if (nrow(group_filtered) == 0) next
      
      # Bootstrap BSS
      boot_obj <- boot(data = group_filtered,
                       statistic = function(d, i) bootstrap_bss(d, i, model_var, ref_prob),
                       R = 500, parallel = "snow")
      
      ci <- boot.ci(boot_obj, type = "perc")
      
      bss_results[[length(bss_results) + 1]] <- tibble(
        Subgroup_Var = subgroup_var,
        Subgroup_Level = group_name,
        Model = model_var,
        BSS_mean = mean(boot_obj$t),
        BSS_ci_lower = ci$percent[4],
        BSS_ci_upper = ci$percent[5]
      )
    }
  }
}


# Combine into a single dataframe
bss_df <- bind_rows(bss_results)
print(bss_df)



summary(group_filtered$x_nomo)
summary(group_filtered$grninf_num)
ref_prob
brier_score(group_filtered$x_nomo, group_filtered$grninf_num)



```
